### 2016-09-06 MSR-design.tex
Change references to match new bib in tex file.

\documentclass{article}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cleveref}

\graphicspath{{./figures/}}

\begin{document}
\section{Comprehensive, expensive (3D) models}
\subsection{MSBR}

The most detailed report on ORNL's molten salt breeder reactor is the technical
report by Robertson. \cite{robertson1971conceptual} A nice overview of the MSBR
geometry is shown in \cref{fig:vertical,fig:horizontal,fig:zoom_horiz}.

@@

\section{Simplified models}
\subsection{MSBR children}
\subsubsection{Cammi et. al.}
This model is based on the multi-physics model by \cite{cammi2011multi}.

>>>>

\documentclass{article}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cleveref}
\graphicspath{{./figures/}}

\begin{document}

\section{Comprehensive, expensive (3D) models}

\subsection{MSBR}

The most detailed report on ORNL's molten salt breeder reactor is the technical
report by Robertson. \cite{robertson_conceptual_1971} A nice overview of the
MSBR geometry is shown in \cref{fig:vertical,fig:horizontal,fig:zoom_horiz}.

@@

\section{Simplified models}

\subsection{MSBR children}

\subsubsection{Cammi et. al.}

This model is based on the multi-physics model by
\cite{cammi_multi-physics_2011}.
